---
title: "Text Mining"
subtitle: " Task 1 & 2 "
author: "Xiang Li"
date: "12/3/2021"
output: 
  pdf_document:
  latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE )
library(gutenbergr)
library(dplyr)
library(stringr)
library(tidyr)
library(tidytext)
library(textdata)
library(tnum)
library(ggplot2)
library(magrittr)
library(utils)
library(wordcloud)
library(reshape2)
library(gridExtra)
library(magrittr)
library(tidyverse)
```
# Task 1

I choose `My Doggie and I`by R.M.Ballantyne as the resource of my text analysis.`My Doggie And I`tells the story of John Mellon (almost a doctor in chapter one) and what happens to him after he meets a certain little canine. This story surrounds a child waif, a young woman, a young gentleman doctor, and an elderly lady. This tale unfolds the story of a bond that brings these unlikely friends together and merges their separate paths of life into one common path. 

```{r}
data(stop_words)
doggie <- gutenberg_download(21752)
# add linenumber
tidy_doggie_Book <- doggie %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  unnest_tokens(word, text)

tidy_doggie <- doggie %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)
```

First, let us get a basic sense of most commoon word in the book.
```{r fig.width=6, fig.height=4,fig.align = "center", fig.cap=" A visualization of the most common words"}
tidy_doggie%>%
  count(word, sort = TRUE) %>%
  filter(n > 45) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n , word)) +
  geom_col() +
  labs(y = NULL)+
  ggtitle("Plot of most common words")


```


```{r}
#get sentiments analysis and explore three dictionaries

#get_sentiments("afinn")
#get_sentiments("bing")
#get_sentiments("nrc")

#nrc_joy <- get_sentiments("nrc") %>% 
 # filter(sentiment == "joy")
#tidy_doggie %>%
#  inner_join(nrc_joy) %>%
 # count(word, sort = TRUE)
```
# Task 2- Bag of Words Analysis

With several options for sentiment lexicons, we can use inner_join() to calculate the sentiment in different ways. Following the step in `Textmining in R`, I choose three general-purpose lexicons are
            *AFINN from Finn Årup Nielsen,
            *bing from Bing Liu and collaborators, and
            *nrc from Saif Mohammad and Peter Turney.
and generat three plot which showed an estimate of the net sentiment (positive - negative) in each chunk of the novel text for each sentiment lexicon.

```{r fig.width=6, fig.height=4,fig.align = "center", fig.cap="visualization of an estimate of the net sentiment (positive - negative) for each sentiment lexicon"}
afinn <- tidy_doggie_Book %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 20) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
  tidy_doggie_Book %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al."),
  tidy_doggie_Book %>% 
    inner_join(get_sentiments("nrc") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    ) %>%
    mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 20, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```
Discussion:

# Task 2 Extra credit
The additional lexicons I found is that `loughran`. And here is the sentiment flow of the book.
```{r}

loughran <- tidy_doggie_Book %>% 
    inner_join(get_sentiments("loughran") %>% 
                 filter(sentiment %in% c("positive", 
                                         "negative"))
    )%>%
  mutate(method = "loughran") %>%
  count(method, index = linenumber %/% 10, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

loughran %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE)


```
Discussion:

```{r}
#Most common positive and negative words

bing_word_counts <- tidy_doggie_Book %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

#bing_word_counts

bing_word_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 15) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)

```

```{r}
#Worldclouds

 tidy_doggie_Book%>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))

```

```{r}
tidy_doggie_Book %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```



